---
title: "COMPSCIX 415.2 Homework 9/Final"
author:  Ken Vo
date:  4-5-19
output:
  html_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
My Github repository for my assignments can be fournd at this URL:  https://github.com/pithunder/compscix-415-2-assignements

## Loading Libraries
```{r load_packages, warning=FALSE, message=FALSE}

library(tidyverse)
library(broom)
```

## EXERCISE 1 - Step 1

```{r}
# sample size
samp_size <- 50
# set the rate parameter
samp_rate <- 1/10000

sample_mean <- sample_sd <- list()

samp_funct <- function(samp_size, samp_rate) {
  # take sample
  take_sample <- rexp(samp_size, samp_rate)
  sample_mean <- mean(take_sample)
  sample_sd <- sd(take_sample)
  my_stat <- list(sample_mean, sample_sd)
  return(my_stat)
}

message("The list for the mean and standard deviation is " )
samp_funct(samp_size, samp_rate)
```

## EXERCISE 1 - Step 2
```{r}

# sample size
samp_size <- 50
# set the rate parameter
samp_rate <- 1/10000

n <- 1000 #how many samples
sample_means <- sample_sds <- rep(NA, n) # empty vector for saving coefficients

samp_fun <- function(samp_size, samp_rate){
for(i in 1:n) {
  take_sample <- rexp(samp_size, samp_rate)
  sample_means [i] <- mean(take_sample)# store the mean
  sample_sds [i] <- sd(take_sample)# store the mean
}
all_results <- tibble(sample_means, sample_sds)
return (all_results)
}

samp_fun (samp_size, samp_rate)
```

## EXERCISE 1 - Step 3

```{r}

ggplot(samp_fun(samp_size, samp_rate)) +
  geom_histogram(mapping=aes(sample_means), bins=30)

stdev_of_sample_means <- sd(samp_fun(samp_size, samp_rate)$sample_means)
message ("The standard deviation of the sample means is ", round(stdev_of_sample_means, digits=2))
theoretical_standard_error <- 10000/sqrt(samp_size)
message ("The theoretical standard error is ", round(theoretical_standard_error,digits=2))

mean_of_sample_sds <- mean(samp_fun(samp_size, samp_rate)$sample_sds)
message ("The mean of the sample standard deviations is ", round(mean_of_sample_sds,digits=2))

emp_stand_error <- mean_of_sample_sds/sqrt(samp_size)
message ("The empirical standard error is ", round(emp_stand_error,digits=2))

```

## EXERCISE 1 - Step 4
```{r}

# sample size
samp_size_step4 <- 5000
# set the rate parameter
samp_rate_step4 <- 1/10000

n <- 1000 #how many samples
sample_means_step4 <- sample_sds_step4 <- rep(NA, n) # empty vector for saving coefficients

samp_fun_step4 <- function(samp_size_step4, samp_rate_step4){
for(i in 1:n) {
  take_sample_step4 <- rexp(samp_size_step4, samp_rate_step4)
  sample_means_step4 [i] <- mean(take_sample_step4)# store the mean
  sample_sds_step4 [i] <- sd(take_sample_step4)# store the mean
}
all_results_step4 <- tibble(sample_means_step4, sample_sds_step4)
return (all_results_step4)
}

samp_fun_step4 (samp_size_step4, samp_rate_step4)

ggplot(samp_fun_step4(samp_size_step4, samp_rate_step4)) +
  geom_histogram(mapping=aes(sample_means_step4), bins=30)

stdev_of_sample_means_step4 <- sd(samp_fun_step4(samp_size_step4, samp_rate_step4)$sample_means_step4)
message ("The standard deviation of the sample means is ", round(stdev_of_sample_means_step4, digits=2))

theoretical_standard_error_step4 <- 10000/sqrt(samp_size_step4)
message ("The theoretical standard error is ", round(theoretical_standard_error_step4,digits=2))

mean_of_sample_sds_step4 <- mean(samp_fun_step4(samp_size_step4, samp_rate_step4)$sample_sds_step4)
message ("The mean of the sample standard deviations is ", round(mean_of_sample_sds_step4,digits=2))

emp_stand_error_step4 <- mean_of_sample_sds_step4/sqrt(samp_size_step4)
message ("The empirical standard error is ", round(emp_stand_error_step4,digits=2))

```

## EXERCISE 2

```{r}
fl_pth_train <- "C:/Users/moi/Documents/R/compscix-415-2-assignments-master/train.csv"
train <- read_csv(file=fl_pth_train)

mod_saleprice <- lm(SalePrice ~ LotArea + OverallQual + ExterQual, data = train)
tidy(mod_saleprice)
glance(mod_saleprice)

```
For every extra square foot in the lot area, the sale price increases, on average, by $1.45, with all other features being held constant.

For every one unit increase in the overall quality of the house, the mean increase in the sale price is $34466.

Using the glance command to output the Rsquared, shows the Rsquared of this model (0.69) is poorer than the Rsquared of the model fitted in HW 7 with GrLivArea, OverallQual, Neighborhood (0.79).

## EXERCISE 3.a

The proportion of visitors converted for version A is 0.0415.
The proportion of visitors converted for version b is 0.1.

```{r}
fl_pth_ab <- "C:/Users/moi/Documents/R/compscix-415-2-assignments-master/ab_test_data.csv"
ab <- read_csv(file=fl_pth_ab)

a <- ab %>% filter(version=='A') # getting version A data only
a_count <- count(a)
a1 <- a %>% filter(conversion==1) # filtering converted 
a1_count <- count(a1) # produces 83
A_conv_rate <- a1_count/a_count # calculating the conversion rate for version A
message("Conversion rate of website A = ", A_conv_rate)


b <- ab %>% filter(version=='B') # getting version B data only
b_count <- count(b)
b1 <- b %>% filter(conversion==1)# filtering converted 
b1_count <- count(b1) # produces 200
B_conv_rate <- b1_count/b_count # calculating the conversion rate for version B
message("Conversion rate of website B = ", B_conv_rate)

```
## EXERCISE 3.b
```{r}
# x is number of successes (conversions)
# n is size of sample
# p is our null hypothesized value
prop_test_A <- prop.test(x = 83, n = 2000, p = .0415)
prop_test_A$p.value

prop_test_B <- prop.test(x = 200, n = 2000, p = .10)
prop_test_B$p.value

true_a <- .0415
true_b <- .1
n_a <- 2000
n_b <- 2000
# this part will simulate how many conversions there are
# for our 1000 visitors, when we know the true conversion rates
# n = 1 because we only want one sample conversion rate
set.seed(10)
samp_a <- rbinom(n = 1, size = n_a, prob = true_a)

samp_b <- rbinom(n = 1, size = n_b, prob = true_b)

two_prop_test <- prop.test(c(samp_a, samp_b), c(1000, 1000))
two_prop_test$p.value

```


